### 2023-10-23 thesis/chapters/03-design.tex
Refactor feature selection methods and finish correletion ranking

>>>>

\section{Measurment strategy}
Describe technical inspection in VNET, a.s. datacentres (DC Digitalis, SHC\rom{2}) from 12th October 2023
and

HVAC - Air conditioning, Refrigirator
Devices:
	- Adiabatic plunger pump: better candidates because of fraquent faults, datacentere is inspected daily and maintaned regulary so it is not that critical, turns off under 26°C to save electricity consumption in winter, we do not have faulty machines for comparision

	- Scroll compressor: example Copeland ZR16M3E-TWD-561 (2900 RPM @ 50 Hz; 9,7 kW (13 HP); 380/420V; 25 A) 3500 RPM @ 60Hz

	Faults (\url{https://www.mdpi.com/1099-4300/17/10/7076})
	- unbalance of the rotor, fault of the scroll, mechanical assembly loose, bearing loose

	- Fig: insert image of cut of compressor
	- Fig: insert spectrograms, orbitals from exploratory measurements

- How to obtain dataset (plan had to been aggreed to by datacentre technician)
 	- every 2 or 3 weeks (4 - 6 times)
 	- 60 - 90 s recordings in each place
  	- good and bad compressor (4 x top, 4x side, 1x base)

\section{Embedded system for dataset measurement}	
Functional requirements
\begin{itemize}
	\item MCU has interface to accept commands and storage to save measurements
	\item Driver for accelerometer is build in
	\item Accelerometer has frequency response at least 500 Hz (FS = min. 3200 Hz)
\end{itemize}
Business (management) requirements: because of time constraints before first technical inspection: build from parts already on stock or inexpensive and quickly procurable, driver should be available, easily save massive recordings to persistant storage, extensible platform in case better option would not be avaiable in the future

Hardware parts:
Faster than target device to enable experimentation, ARM platform
\begin{itemize}
	\item Beaglebone Black 
		(Texas Instruments Sitara AM3358: 1GHz ARM Cortex-A8, 
		 SDRAM: 512MB DDR3L 800MHZ, 
		 Onboard Flash: 4GB)
	\item OS: Debian 10 Kernel 5.10.168-ti-r72
	\item Accelerometer ADXL335, 3-Axis $\pm$3 g Accelerometer, 
	      Bandwidths X, Y axes: (0.5 Hz - 1.6 kHz), Z axes: (0.5 Hz - 0.55 kHz)
	  (via 8 channel 12-bit SAR ADC, 1.8V, 200 MSPS)
	 \item Later: ADXL345 (SPI, ODR: 3.2 kHz) 
\end{itemize}

### 2023-10-23 thesis/chapters/appendix/B-plan-of-work.tex
Refactor feature selection methods and finish correletion ranking

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting with the supervisor and consultant to set goals, experiments and discuss status of collaborations with the industry.
\\ \hline
\nth{2} week         &  Arrange collaboration with alternative industry partner. Prepare checklist for technical inspection of machinery. Construct device (BeagleBone Black + ADXL335) for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in data centre of the industry partner. Calculate features from Mafaulda dataset and start feature selection
 \\ \hline
\nth{4} week         & Consultation with the supervisor about choice of machine to measure (scroll compressor), device for measurement, and requirements for dataset gathering. Feature selection methods comparison on Mafaulda dataset.
 \\ \hline
\nth{5} week         & Make further exploratory measurements with rewritten code ensuring more precise accelerometer sampling. Make a plan of measurement and negotiate it with industry partner. Feed exporatory dataset into anomaly detection models.
 \\ \hline
\nth{6} week         & 
 \\ \hline
\nth{7} week         &
 \\ \hline
 \nth{8} week         & 
 \\ \hline
 \nth{9} week         & 
 \\ \hline
  \nth{10} week         & 
 \\ \hline
  \nth{11} week         & 
 \\ \hline
  \nth{12} week         & 
 \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting with the supervisor and consultant to set goals, experiments and discuss status of collaborations with the industry.
\\ \hline
\nth{2} week         &  Arrange collaboration with alternative industry partner. Prepare checklist for technical inspection of machinery. Construct device for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in data centre of the industry partner. Feature extraction: calculate features from Mafaulda dataset.
 \\ \hline
\nth{4} week         & Consultation with the supervisor about choice of machine to measure (scroll compressor), device for measurement, and requirements for dataset gathering. Fine tune measurement device.
 \\ \hline
\nth{5} week         &  Feature selection: create procedures to determine sets of best data features in Mafaulda dataset.
 \\ \hline
\nth{6} week         & Generate comprehensive reports from jupyter notebooks. Mafaulda feature sampling for kNN multiclass classification.
 \\ \hline
\nth{7} week         & ?Consultation with the supervisor ... Feed exporatory dataset into anomaly detection models.
 \\ \hline
 \nth{8} week         & 
 \\ \hline
 \nth{9} week         & ??Make further exploratory measurements with rewritten code ensuring more precise accelerometer sampling. Make a plan of measurement and negotiate it with industry partner.
 \\ \hline
  \nth{10} week         & ?Begin writing implementation
 \\ \hline
  \nth{11} week         & 
 \\ \hline
  \nth{12} week         & 
 \\ \hline
\end{tabular}
\end{table}
